The Effect of Events on Australian Parliamentary Discussion (1851--2017)

### 2018-10-13 outputs/docs/events/paper.Rmd
Fix compilation issues

yearsUsed <- read_csv(here::here("outputs/misc/years_used.csv"), col_types = cols()) %>% 
  replace_na(list(Parliament = ""))
elections <- read_csv(here::here("inputs/misc/misc_elections_data.csv"), col_types = cols())
governments <- read_csv(here::here("inputs/misc/change_of_pm.csv"), col_types = cols())
keyEvents <- read_csv(here::here("inputs/misc/key_events.csv"), col_types = cols())
significances <- read_csv(here::here("outputs/misc/significance.csv"), col_types = cols())
top_words <- read_csv2(here::here("outputs/misc/top_words.csv"), col_types = cols())
missing_days <- read_csv(here::here("outputs/misc/missing_days.csv"), col_types = cols())
hansard_sources <- read_csv(here::here("outputs/misc/hansard_sources.csv"), col_types = cols())

@@

$$
\gamma_{t,} &\sim \mbox{Dirichlet}(\mu_{s[t],})
$$
This distributional assumption accounts for the fact that on any given day, the sum of all proportions in each topic must equal 1.

>>>>

yearsUsed <- read_csv(here::here("outputs/misc/years_used.csv"), col_types = cols()) %>% 
  replace_na(list(Parliament = ""))
elections <- read_csv(here::here("inputs/misc/misc_elections_data.csv"), col_types = cols())
governments <- read_csv(here::here("inputs/misc/change_of_pm.csv"), col_types = cols())
keyEvents <- read_csv(here::here("inputs/misc/key_events.csv"), col_types = cols())
significances <- read_csv(here::here("outputs/misc/significance.csv"), col_types = cols())
top_words <- read_csv2(here::here("outputs/misc/top_words_40.csv"), col_types = cols())
missing_days <- read_csv(here::here("outputs/misc/missing_days.csv"), col_types = cols())
hansard_sources <- read_csv(here::here("outputs/misc/hansard_sources.csv"), col_types = cols())

@@

$$
\gamma_{t,} \sim \mbox{Dirichlet}(\mu_{s[t],})
$$
This distributional assumption accounts for the fact that on any given day, the sum of all proportions in each topic must equal 1.
